### 2021-10-20 paper/paper.tex
added a paragraph at the end to say large test case counts are deceiving

\section{Conclusion}
Combinatorial interaction testing is an advanced technique because it's tailored to a difficult situation, when you can't afford not to spend the time to make your best guess at test cases. However, this kind of automation is easy to specify and run in Julia's ecosystem. The most difficult part of the transition to automated test case generation is shifting from manually-computed checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}. A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation. They point to the broad applicability of automation for testing and the effectiveness of tools that offer control to the test author.

>>>>

\vskip 6pt
All of these approaches to automated test generation create more tests with less code than manual alternatives. This makes a test suite less brittle as the code-under-test is modified. It can also create test suites with a reassuring number of test cases, but none of the automated techniques above remove risk. We still need to rely on software engineering techniques, such as tracking of historical bug report rates, in order to understand the maturity of a code base.

\section{Conclusion}
Combinatorial interaction testing is an advanced technique because it's tailored to a difficult situation, when you can't afford not to spend the time to make your best guess at test cases. However, this kind of automation is easy to specify and run in Julia's ecosystem. The most difficult part of the transition to automated test case generation is shifting from manually-computed checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}. A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation. They point to the broad applicability of automation for testing and to the effectiveness of tools that offer control to the test author.
